\textsc{spiderman}: an open source code to model phase curves and secondary eclipses.

### 2016-09-26 ms.tex
added plots
started to write some discussion

% Only include extra packages if you really need them. Common packages are:
\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{bmpsize}
\usepackage[anythingbreaks]{breakurl}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[SPIDERMAN]{SPIDERMAN}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. Louden, L. Kreidberg]{Tom Louden$^{1}$\thanks{E-mail: t.m.louden@warwick.ac.uk} and Laura Kreidberg$^{2}$\\
$^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
$^{2}$Department of Physics, University of America, America, America, America}

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

@@

@@

@@

\section{Observations}\label{sec:Observations}

@@

@@

@@

\section{Results}\label{sec:results}

@@

\subsection{transmission spectra}

\subsection{Updated system parameters}\label{sec:system}

@@

\subsection{Spot crossing event}\label{sec:spotcross}

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{bmpsize}
\usepackage[anythingbreaks]{breakurl}
\usepackage{subfig}
\usepackage{fancyvrb}
\usepackage{hyperref}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[spiderman]{\textsc{spiderman}: an open source code to model phase curves and secondary eclipses.}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. Louden, L. Kreidberg]{Tom Louden$^{1}$\thanks{E-mail: t.m.louden@warwick.ac.uk} and Laura Kreidberg$^{2}$\\
$^{1}$Department of Physics, University of Warwick, Coventry, CV4 7AL, UK\\
$^{2}$Department of Astronomy, Harvard, America, America, America}

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2016}

@@

Presenting \textsc{spiderman}, a fast code for calculating exoplanet phase curves and secondary eclipses with arbitrary surface brightness distributions.

The development version of the code is available at \url{https://github.com/tomlouden/spiderman}.

@@

\textsc{spiderman}

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/sphere_quad.pdf}
\includegraphics[width=\columnwidth]{img/spherical_lc.pdf}
\caption{A model generated using spherical harmonics}
\label{fig:harmonics}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/zhang_lc_zoom.pdf}
\caption{This is a caption}
\label{fig:extract_region}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/free_parameterstriangle.pdf}
\caption{This is a caption}
\label{fig:extract_region}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
\includegraphics[width=\columnwidth]{img/free_parametersflux_map.pdf}
\includegraphics[width=\columnwidth]{img/free_parametersflux_errs.pdf}
\caption{left: right: the constraints on the brightness distribution.}
\label{fig:extract_region}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\columnwidth]{img/free_parameterstemp_map.pdf}
\includegraphics[width=\columnwidth]{img/free_parameterstemp_errs.pdf}
\caption{The underlying temperature distributions generated by the zhang model.}
\label{fig:extract_region}
\end{center}
\end{figure*}

@@

\section{The \textsc{spiderman} package}\label{sec:package}

\textsc{spiderman} is an open source project and is being actively developed on github. The code is available on PyPi, and the latest stable version can easily by installed by simply running the command

\begin{Verbatim}[frame=single]
> pip install spiderman-package
\end{Verbatim}

Or, to access the bleeding-edge development version from github:

\begin{Verbatim}[frame=single]
> git clone https://github.com/tomlouden/SPIDERMAN
> cd SPIDERMAN
> sudo python setup.py install
\end{Verbatim}

Full installation instructions and other information are available in the documentation, at \url{http://spiderman.readthedocs.io}

@@

\section{Application to data}\label{sec:Observations}

As a test of the performance of the code the model was applied to a phase curve and secondary eclipse of WASP-43b taken with HST WFC3. These data had previously been published in \citet{Stevenson2014c}. However, in this paper the phase curve and the secondary eclipse are treated as seperate phenomena, when of course, they are both manifestations of the same underlying brightness distribution. Indeed, the bright dayside of the planet is the main driver of the phase curve, and is also the part occulted by the stellar disc. It is therefore more parsimonious, if at all possible, to use a model that accounts for both of these observations simultaneously. This also reduces the total number of paramters needed, which is satisfying from an information content angle.

One could argue that planetary limb darkening, among other effects, will act to decouple the secondary eclipse from the phase curve, and there are not good constraints on what to expect from the limb darkening as it requires a full atmosphere model treatment. However, one would expect that the. \textsc{spiderman} does have the option to include planetary limb darkening, which would allow one to marginalise over the uncertainty in these parameters.

In princple, constraints being placed on the limb darkening can constrain the vertical temperature profile of the planet.

@@

\subsection{Future work}\label{sec:future work}

\textsc{spiderman} is still under development, and there are a number of features that are planned to be implemented:

- More brightness distributions, such as orange segments
- Better treatment of errors in the
